Contextual Combinatorial Cascading Bandits

### 2016-01-14 contextual combinatorial cascading bandits.tex
update experiment

\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

@@

@@

@@

\begin{figure}
	\centering
	\subfigure[Network 1755]{
		\includegraphics[height = 1.8cm, width = 2.6 cm]{network3-1.eps}}
	\subfigure[Network ]{
		\includegraphics[height = 1.8cm, width = 2.6 cm]{network4-1.eps}}
	\subfigure[Network]{
		\includegraphics[height = 1.8cm, width = 2.6 cm]{network4-1.eps}}
	\caption{sample number and accuracy}
	\label{fig:sample number} % 用于交叉引用
\end{figure}

>>>>

\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

@@

In the first experiment, we compare $C^3$-UCB to $C^2$UCB and CombCascade on two synthetic problems. chiao tsing path

Let $\cB = \{x \in \RR^d : \|x\|_2 = 1 \}$ be the unit ball of $\RR^d$ and let $E = \{1,...,L\}$ be the set of all base arms. We randomly choose $\theta_{\ast}$ with $\|\theta_{\ast}\|_2 = 1$ and randomly assign a $\mu_i \in \cB$ to $i$ for any $i \in E$. At each time $t$, $b_{t,i} \in \cB$ is randomly assigned to base arm $i$. Also we fix a constant $h$ to balance weights of $\mu_i$ and disturbance $b_{t,i}$. Let $x_{t,i} = \frac{\mu_i + h b_{t,i}}{\|\mu_i+h\cdot b_{t,i}\|_2}$ be the context of base arm $i$ at time $t$. And the weight for base arm $i$ at time $t$ is $w_t(i) = \theta_{\ast}^{\top}x_{t,i} + \epsilon_{t,i}$ where $\epsilon_{t,i} \sim N(\mu_i, \sigma_i)$ for fixed $\sigma_i$.

@@

In this experiment, we evaluate $C^3$-UCB on a problem of contextual recommendations. We experiment on {\it MovieLens} dataset\cite{lam2013movie} of March 2015.

The Learning problem is formulated as follows. There is a big sparse matrix $A \in \{0,1\}^{N_u \times N_m}$ where $A(u,m) = 1$ denotes user $u$ has watched movie $m$.We split $A$ to be $H + F$ by putting entry-$1$ of $A$ to $H$ and $F$ with probability $\sim \mathrm{Ber}(p)$ for some fixed $p$. We can regard $H$ as know information about history 'What users have watched' and regard $F$ as future criterion. We use $H$ to derive feature vectors of both users and movies by SVD decomposition $H = USV^{\top}$ where $U = (u_1; ...;u_M)$ and $V = (v_1;...;v_L)$. At every time $t$, use $x_{t,i} = u_{i}v_j^{\top}$ as the context information of base arm $i$ and randomly choose a user $I_t$. And use $w_t(j) = F(I_t,j)$ as the weight of base arm $j$.

Notice that for this case, fixed number of base arms, it might have problem if we use $(u_{I_t}, v_j)$ as context information.
Since to find the best arm, it is equivalent to find the best one with highest weights sum, so is equivalent to the best one with highest $\theta_{v}^{\top}x$.

\begin{figure}
	\centering
	\subfigure[MovieLens]{
		\includegraphics[height = 3cm, width = 5 cm]{movie-1.eps}}
	\caption{MovieLens}
	\label{fig:movielens} % 用于交叉引用
\end{figure}

@@

\begin{figure*}
	\centering
	\subfigure[Network 1221]{
		\includegraphics[height = 3 cm, width = 5 cm]{network1-1.eps}}
	\subfigure[Network 1755]{
		\includegraphics[height = 3 cm, width = 5 cm]{network3-1.eps}}
	\subfigure[Network 3257 ]{
		\includegraphics[height = 3 cm, width = 5 cm]{network4-1.eps}}
	\caption{Network with latency}
	\label{fig:sample number} % 用于交叉引用
\end{figure*}
